What we {\sf eval} in the shadows

### 2021-04-01 paper/main.tex
methodology

Our corpus is assembled out of two set of programs, one consisting of libraries
obtained from \emph{CRAN} (Comprehensive R Archive Network\footnote{CRAN is the
  largest repository of R code with almost \CranAvailablePackagesRnd packages.
  It receives about 6 new package submissions a day~\cite{Ligges2017}. \cf
  \url{https://cran.r-project.org}}) and the other from
the \emph{Kaggle} data science competition website\footnote{\cf
  \url{https://kaggle.com}}. The intent here is to contrast code written by
experienced developers (CRAN) with code authored by typical end users of the
language (Kaggle). Another difference is that CRAN is a curated repository. Each
submitted package must abide to a number of well-formedness rules that are
automatically checked asserting certain quality. Most relevant for this work is
that all of the runnable code is tested and only a successfully running package
is admitted in the archive. Kaggle on the other hand is more like GitHub, anyone
can submit any code. All the code in our corpus is runnable, \ie we have scripts
that invoke the CRAN packages and the Kaggle programs have input data.

\mypara{Packages.} We obtained \CranAllPackages packages from CRAN, only
excluding packages that did not install due to missing native dependencies.
Using \c{cloc}, we measured \CranAllRCodeRnd lines of R and
\CranAllNativeCodeRnd lines of native code. Out of these packages, \CranPackages
(\CranPackagesRatio) call eval. These packages represent \CranCodeRatio of the
code size. To analyze a package, we need client code that invokes its methods.
There are three sources of built-in runnable code that come with each CRAN
package: \emph{tests, examples} and \emph{vignettes}. They are, respectively,
traditional unit tests, code snippets from the documentation, and long-form
use-cases written in \LaTeX\xspace or Markdown with executable snippets of R
code. Examples and vignettes are automatically extracted and turned into
scripts, their input is bundled with the package. Tests are directly runnable.
Together we there are \CranRunnableScripts scripts that contain
\CranRunnableCode lines of code (\CranRunnableCodeExamplesRnd in examples,
\CranRunnableCodeVignettesRnd in vignettes and \CranRunnableCodeTestsRnd in
tests).

\mypara{Scripts.} Kaggle is an online platform for data science. It allows users
to submit problems and compete to solve them. Solutions, called \emph{kernels},
are uploaded as plain scripts or notebooks. We obtained \KaggleKernels kernels.
Since Kaggle is not curated, used SHA-1 hashes to identify and remove
\KaggleDuplicates duplicate entries. The remaining \KaggleUnique kernels are
unique solutions to \KaggleCompetitions competition. They contain \KaggleCode
lines of R code. Only \KaggleWithEvals kernels  call \eval.

>>>>

Our corpus is assembled from three sources. Firstly, we start with the
\emph{Base} libraries that are bundled with the language implementation.
Secondly, we acquire packages hosted on \emph{CRAN}. Thirdly, we downloaded
scripts from \emph{Kaggle}.

\mypara{Base.}
???

\mypara{CRAN.} The Comprehensive R Archive
Network,\footnote{\url{cran.r-project.org}} or CRAN, is the largest curated
repository of R packages. It hosts \CranAvailablePackagesRnd packages with 6 new
packages submitted each day~\cite{Ligges2017}. Packages that are accepted to
CRAN are authored by experienced developers and they must abide to a number of
well-formedness rules automatically checked on each commit. Furthermore, each
package comes with sample data and tests. There are three sources of runnable
code for each package: \emph{tests, examples} and \emph{vignettes} --
respectively, unit tests, executable code snippets from the documentation, and
long-form executable use-cases written in Markdown. Examples and vignettes can
be turned into scripts by extracting the relevant code. We obtained
\CranPackages that call \eval. These packages represent \CranPackagesRatio of
all packages or \CranCodeRatio of the entire code size of CRAN. From these we
extracted \CranRunnableScripts scripts that contain \CranRunnableCode lines of
code (\CranRunnableCodeExamplesRnd in examples, \CranRunnableCodeVignettesRnd in
vignettes and \CranRunnableCodeTestsRnd in tests).

\mypara{Scripts.} Kaggle is an online platform for data
science.\footnote{\url{kaggle.com}} It allows users to submit problems and
compete to solve them. Solutions, called \emph{kernels}, are uploaded as plain
scripts or notebooks. The quality of code on Kaggle is not uniform. Each kernel
is runnable, and thus there is one script per kernel. Input data is provided.
We obtained \KaggleKernels kernels.
Since Kaggle is not curated, used SHA-1 hashes to identify and remove
\KaggleDuplicates duplicate entries. The remaining \KaggleUnique kernels are
unique solutions to \KaggleCompetitions competition. They contain \KaggleCode
lines of R code. Only \KaggleWithEvals kernels  call \eval.
